---
title: "Causal inference"
format: html
---

# Introduction

This is the first Quarto document of causal inference using machine learning such as Meta learner.

## Methods

The lalonde dataset is simultaneously RCT and observational study.
We hypothesized that ATT in observational study is nearest ATE in RCT. 
The estimate value in RCT is 800-900 dollars.

by "https://causalinf.substack.com/p/lalonde-40-years-later-imbens-and"

### import packages

```{r}
library(languageserver)
library(httpgd)

```
### read lalonde dataset

```{r}
library(MatchIt)
lalonde_r <- MatchIt::lalonde

```

## regression model

```{r}
library(parameters)
library(rms)

dd <- datadist(lalonde_r)
options(datadist = "dd")

fit_ols <- rms::ols(re78 ~ treat + age + educ + race + married + nodegree + re74 + re75, data = lalonde_r)

fit_ols_rcs <- rms::ols(re78 ~ treat + rcs(age, 5) + educ + race + married + nodegree + rcs(re74, 5) + rcs(re75, 5), data = lalonde_r)

parameters::compare_parameters(fit_ols, fit_ols_rcs, keep = "treat")

```

## Propensity score matching and weighting

```{r}
library(parameters)
library(highs)
library(MatchIt)
library(rootSolve)
library(WeightIt)
library(cobalt)
library(marginaleffects)
library(broom)

mout <- MatchIt::matchit(
    treat ~ age + educ + race + married + nodegree + re74 + re75, 
    data = lalonde_r, 
    method = "cardinality", 
    distance = "glm", 
    estimand = "ATT"
    )

cobalt::bal.tab(mout)

mdata <- MatchIt::match.data(mout)

fit_match_pre <- lm(re78 ~ treat * (age + educ + race + married +
                            nodegree + re74 + re75),
          data = mdata,
          weights = weights)


fit_match <- avg_comparisons(fit_match_pre,
                variables = "treat",
                vcov = ~subclass)


wout <- WeightIt::weightit(
    treat ~ age + educ + race + married + nodegree + re74 + re75, 
    data = lalonde_r, 
    method = "ipt",
    estimand = "ATT"
)                

cobalt::bal.tab(wout)


fit_weight_pre <- lm_weightit(re78 ~ treat * (age + educ + race + married +
                                     nodegree + re74 + re75),
                   data = lalonde_r, weightit = wout)

fit_weight <- avg_comparisons(fit_weight_pre,
                variables = "treat")           


modelbased::estimate_contrasts(
    fit_weight_pre, 
    contrast = "treat", 
    estimate = "population"
)      

modelsummary::modelsummary(
    list("PS match" = fit_match, 
    "PS weight" = fit_weight)
)

```

```{r}
library(dplyr)
library(grf)

X <- model.matrix(~ age + educ + race + married + nodegree + re74 + re75 + 0, data = dplyr::select(lalonde_r, -re78, -treat))
Y <- lalonde_r$re78
W <- lalonde_r$treat

fit_grf <- grf::causal_forest(X = X, Y = Y, W = W)

grf::average_treatment_effect(fit_grf, target.sample = "overlap")

```

```{r}
library(dplyr)
library(tmle)

W <- model.matrix(~ age + educ + race + married + nodegree + re74 + re75 + 0, data = dplyr::select(lalonde_r, -re78, -treat))

Y <- lalonde_r$re78
A <- lalonde_r$treat

tmle_fit <- tmle::tmle(Y = Y, A = A, W = W, 
    family = 'gaussian', 
    Q.SL.library=c("SL.mean","SL.glm"),
    g.SL.library=c("SL.mean","SL.glm"),
    Qform = "Y~A+age+educ+raceblack+racehispan+racewhite+married+nodegree+re74+re75", 
    gform = "A~age+educ+raceblack+racewhite+racehispan+married+nodegree+re74+re75", 
    cvQinit = TRUE)

summary(tmle_fit)

```

```{r}
library(dplyr)
library(AIPW)
library(easystats)

AIPW_SL <- AIPW$new(Y= lalonde_r$re78,
                    A= lalonde_r$treat,
                    W= subset(lalonde_r,select=c("age", "educ", "race", "married", "nodegree", "re74", "re75")), 
                    Q.SL.library = c("SL.glm"),
                    g.SL.library = c("SL.glm"),
                    k_split = 5,
                    verbose=TRUE)
                
  suppressWarnings({
  AIPW_SL$fit()$summary(g.bound = 0.025)
})


  suppressWarnings({
  AIPW_SL$stratified_fit()$summary(g.bound = 0.025)
})


tmle_fit <- tmle::tmle(Y = Y, A = A, W = W, 
    family = 'gaussian', 
    Q.SL.library=c("SL.mean","SL.glm"),
    g.SL.library=c("SL.mean","SL.glm"),
    Qform = "Y~A+age+educ+raceblack+racehispan+racewhite+married+nodegree+re74+re75", 
    gform = "A~age+educ+raceblack+racewhite+racehispan+married+nodegree+re74+re75", 
    cvQinit = TRUE)


cat("\nEstimates from TMLE\n")
unlist(tmle_fit$estimates$ATE)
unlist(tmle_fit$estimates$RR)
unlist(tmle_fit$estimates$OR)

cat("\nEstimates from AIPW\n")

a_tmle <- AIPW_tmle$
  new(
    Y= lalonde_r$re78,
    A= lalonde_r$treat,
    tmle_fit = tmle_fit, 
    verbose = TRUE)$
  summary(g.bound=0.025)

```



```{r}

library(reticulate)


```

```{python}

import pandas as pd
import polars as pl
import tableone
import marginaleffects

```

```{r}
library(MatchIt)
lalonde_r <- MatchIt::lalonde
```


```{python}
import matplotlib.pyplot as plt
import seaborn as sns

lalonde_py = r.lalonde_r

lalonde_py.describe()

sns.scatterplot(data = lalonde_py, x = 're74', y = 're78', hue = 'treat')

plt.show()

```

```{python}
import statsmodels.formula.api as smf

formu = 're78 ~ treat + age + educ + race + married + nodegree + re74 + re75'

ols_fit = smf.ols(formula=formu, data = lalonde_py).fit()

ols_fit.summary()
```

```{python}
import pandas as pd
import dowhy
from dowhy import CausalModel

lalonde_post = (pd.get_dummies(lalonde_py, 
                         columns=["race"], dtype=int)          
)

model = CausalModel(
    data=lalonde_post,
    treatment="treat",
    outcome="re78",
    common_causes=["age", "educ", "married", "nodegree", "re74", "re75", "race_black", "race_hispan", "race_white"],
    instruments=None)

model.summary()

```

### read data

```{python}
# rhc = pd.read_csv('rhc.csv')
# rhc.head()
# rhc.describe()
```

